Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-12 paper/paper.tex
edits section 2 and 3
pass on findings and lessons

\section{Engines Studied}
\label{sec:methodology}
\label{sec:methodology:engines}~We selected
JS engines according to the following criteria: 1) Released latest
version after Jan 1, 2018, 2) Contains more than 1K stars on GitHub,
and 3) Uses a public issue tracker. We looked for highly-maintained
(as per the first criterion) and popular (as per the second criterion)
engines. As we wanted to report bugs, we also looked for project with
public issue trackers. Table~\ref{tab:engines} lists the engines we
analyzed. It is worth noting that we used Google Chrome Lab's JSVU
tool~\cite{jsvu} to automatically install and configure versions of
different JS engines in our host environment. This is important as we
aim to use the most recent stable versions of each engine as to avoid
reporting old and already-fixed bugs to developers.

@@

\section{Case Study: \hermes}
\label{sec:bugs}

@@

\subsection{Key Findings and Lessons}
\label{sec:lessons}

@@

\begin{itemize}
  \item Both techniques we investigated were successful in revealing
    bugs (several of them);
  %% \item We have found more bugs with test transplantation than we have
  %%   with cross-engine differential testing. In addition, test
  %%   transplantation demanded less effort per bug;
  \item Even simple black-box fuzzers can create surprisingly
    interesting inputs. We conjecture that there is room to find more
    bugs using other fuzzers;
  \item Mozilla's \smonkey\ appears to be the most reliable
    \js\ engine we analyzed, with Google's \veight\ after it.
\end{itemize}

The main lessons we learned from this study are as follows: 1)~Even
for software projects with fairly clear specifications, as the case of
\javascript{}~\cite{ecmas262-spec}, there is likely to be (a lot of)
variation between different implementations and, therefore,
opportunities for bugs. 2)~Not only multiple different implementations
can be leveraged in differential testing, but differences in test
suites can also be important. 3)~Finding functional/non-crash bugs
with differential testing is feasible on real, complex, widely used
pieces of software. 4)~Further reducing cost of inspection is an
important problem. Although the inspection activity was not
uninterrupted, it is safe to say that each warning required a
substantial amount of time to analyze for potential false alarms. In
fact, many \hi\ warnings reported with differential testing were not
analyzed. In determining cost, we observed, from experience, that the
complexity of the \js\ specifications that the original test covers
increases cost of diagnosing (as developers need to read and
understand those) and the availability of alternative implementations
(for the cases warnings are revealed through differential testing)
reduces the cost of diagnosis. We prefer to see such problem as an
opportunity for future research. For example, applying learning
techniques to prioritize the warnings more likely to be faulty (in the
spirit of the work of Chen and
colleagues~\cite{Chen:2017:LPT:3097368.3097451}) may be a promising
avenue to explore. Recall that the rate of true positives of the
techniques we studied is rather small.  5)~We learned that reporting
real bugs is a great way to train (and encourage) students in software
testing. Students praised the experience of diagnosing failures,
understanding part of the specs (as needed), writing bug reports,
participating in discussions on issue trackers, and observing the
change of status. That was a relatively self-contained hands-on
activity that enabled students to engage in a real-life serious
industrial project.

@@

%%  LocalWords:  IoT DT JS JIT fuzzer jsfunfuzz jit funfuzz bytecodes
%%  LocalWords:  JavaScriptCore JScript Ecma toPrecision Kangax JSVU
%%  LocalWords:  cccrr WebKit ReferenceError TypeError lineNumber sep
%%  LocalWords:  drainMicrotasks ccrrrr Duktape js runtime formedness
%%  LocalWords:  NN NLP vec embeddings perceptron arrowed toolchain
%%  LocalWords:  fuzzers eshost cli pre ArrayBuffer RangeError getInt
%%  LocalWords:  ToIndex Clusterization byteOffset SpiderMonkey AFL
%%  LocalWords:  DataView setInt Radamsa QuickFuzz Grammarinator de
%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers Breno cccrrr
% LocalWords:  d'Amorim Universidade Pernambuco JerryScript JSI RQ FP
% LocalWords:  WScript conformant TP ccr OME FPs TPs crrrrr ccrr NaN
% LocalWords:  ascii unary ToNumber valueOf eval SyntaxError iterable
% LocalWords:  escapeinside basicstyle boxpos numberstyle assertEq
% LocalWords:  morekeywords typeof instanceof foofoofoo TinyJS SSL
% LocalWords:  TLS Lidbury OpenCL SIMD GPUs Purdom parsers Lammel APQ
% LocalWords:  Shulte Geno XPath combinatorial CSmith LLVM Patra CNPq
% LocalWords:  disassemblers Pradel namespaces Eshkevari FACEPE
% LocalWords:  PRONEX

>>>>

\section{Engines Studied}
\label{sec:methodology}
\label{sec:methodology:engines}~We selected
JS engines according to the following criteria: 1) Released latest
version after Jan 1, 2018, 2) Contains more than 1K stars on GitHub,
and 3) Uses a public issue tracker. We looked for highly-maintained
(as per the first criterion) and popular (as per the second criterion)
engines. As we wanted to report bugs, we also looked for project with
public issue trackers. We initially selected four JS engines:
\jsc, \veight, \chakra, and \smonkey. Additionally, we also included
\hermes in the list of studied engines. The main reason for this was
to investigate how our approach would work on a recently introduced JS
engined. More about \hermes on Section~\ref{sec:hermes}.
Table~\ref{tab:engines} lists the engines we
analyzed. It is worth noting that we used Google Chrome Lab's JSVU
tool~\cite{jsvu} to automatically install and configure versions of
different JS engines in our host environment. This is important as we
aim to use the most recent stable versions of each engine as to avoid
reporting old and already-fixed bugs to developers.

@@

\section{Case Study: \hermes}
\label{sec:hermes}

@@

\subsection{Key Findings}
\label{sec:findings}

@@

\begin{enumerate}
  \item Both techniques we studied have shown to be practical and
    effective to find bugs on real, complex, and widely used software
    systems;
  \item Even for language APIs with fairly clear specs, as it is the
    case of JavaScript, there is likely (a lot of) variation between
    different implementations, which brings intrinsic challenges to
    developers that work on them;
  \item Even simple black-box fuzzers can create surprisingly
    interesting inputs;

\end{enumerate}

%% 3)~Not only multiple different
%% implementations can be leveraged in differential testing, but
%% differences in test suites can also be important.

The main findings of this study are as follows: 1) The techniques we
selected found, with relatively low effort, several bugs even in very
robust engines, such as Mozilla's \smonkey, 2)~Even for software
projects with fairly clear specifications, as the case of
\javascript{}~\cite{ecmas262-spec}, there are lots of undefined
implementation-specific behaviors whose implementation can
inadvertedly lead to interference in the well-specified parts of the
spec, leading to clear bugs. 3)~Finding functional/non-crash bugs with
differential testing is feasible on real, complex, widely used pieces
of software. Even black-box mutational fuzzers revealed bugs. We do
expected that other kinds of fuzzers (\eg{}, graybox fuzzers and
black-box grammar-based generational fuzzers) could reveal even more
bugs

\subsection{Key Lessons}
\label{sec:lessons}

The key lessons of this study are as follows:

\begin{enumerate}
\item The use of Mozilla's \smonkey\ and Google's \veight\ engines
  should be encouraged;
\item The cost of inspection of the warnings in differential testing
  should be reduced;
\item Finding bugs in large software is a very effective way to engage
  student in contributing to open-source software and learning
  Software Testing practices.
\end{enumerate}

1)~When taking into consideration our bug finding campaign, Mozilla's
\smonkey\ and Google's \veight\ stood out as the most reliable
engines. Therefore, we recommend the use of these engine for running
\js\ applications. 2)~Further reducing cost of inspection in
differential testing is an important problem. Although the inspection
activity was not uninterrupted, it is safe to say that each warning
required a substantial amount of time to analyze for potential false
alarms. In fact, many \hi\ warnings reported with differential testing
were not analyzed. We observed empirically that the cost of analysis
was proportional to (i) the \js\ specification covered by the original
test (as developers need to read and understand those parts) and (ii)
the availability of alternative implementations. We prefer to see such
problem as an opportunity for future research. For example, applying
learning techniques to prioritize the warnings more likely to be
faulty (in the spirit of the work of Chen and
colleagues~\cite{Chen:2017:LPT:3097368.3097451}) may be a promising
avenue to explore. Recall that the rate of true positives of the
techniques we studied is rather small. 3)~We learned that reporting
real bugs is a great way to train (and encourage) students in software
testing. Students praised the experience of diagnosing failures,
understanding part of the specs (as needed), writing bug reports,
participating in discussions on issue trackers, and observing the
change of status. That was a relatively self-contained hands-on
activity that enabled students to engage in a real-life serious
industrial project.

@@

%%  LocalWords:  IoT DT JS JIT fuzzer jsfunfuzz jit funfuzz bytecodes
%%  LocalWords:  JavaScriptCore JScript Ecma toPrecision Kangax JSVU
%%  LocalWords:  cccrr WebKit ReferenceError TypeError lineNumber sep
%%  LocalWords:  drainMicrotasks ccrrrr Duktape js runtime formedness
%%  LocalWords:  NN NLP vec embeddings perceptron arrowed toolchain
%%  LocalWords:  fuzzers eshost cli pre ArrayBuffer RangeError getInt
%%  LocalWords:  ToIndex Clusterization byteOffset SpiderMonkey AFL
%%  LocalWords:  DataView setInt Radamsa QuickFuzz Grammarinator de
%%  LocalWords:  LangFuzz Megadeth libFuzzer sanitizers Breno cccrrr
% LocalWords:  d'Amorim Universidade Pernambuco JerryScript JSI RQ FP
% LocalWords:  WScript conformant TP ccr OME FPs TPs crrrrr ccrr NaN
% LocalWords:  ascii unary ToNumber valueOf eval SyntaxError iterable
% LocalWords:  escapeinside basicstyle boxpos numberstyle assertEq
% LocalWords:  morekeywords typeof instanceof foofoofoo TinyJS SSL
% LocalWords:  TLS Lidbury OpenCL SIMD GPUs Purdom parsers Lammel APQ
% LocalWords:  Shulte Geno XPath combinatorial CSmith LLVM Patra CNPq
% LocalWords:  disassemblers Pradel namespaces Eshkevari FACEPE
% LocalWords:  PRONEX
<
